---
title: "My Titanic"
author: Frédéric Bevia
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction | A real Case

At my job, i'm incharge of deploying applications virtualization with the virtualization software Applidis, based on Microsoft TSE/RDP protocol. These virtualized apps are deployed on servers.
One of my task is to monitor theses servers for their activities and the apps activities. So these plot is a firts attempt (a very simple prototype:-) to do that. From a csv file which contains the date and time of the use of applications by servers, i plotted, with plotly the min,max and mean duration of the sum of all apps usage, by Server and by date. 
Further more, i trace two servers particularly:

- SRVMV-COMMUN001
- SRVMV-PDEP001.  

```{r, echo=F, warning=F, message=F}
#load leaflet package for R
library(plotly)
#library(lubridate)
library(chron)

# reusable function for highlighting a particular Serveur or app
layer_server <- function(plot, name) {
  plot %>% filter(Server == name) %>% add_lines(name = name)
}

# reusable function for plotting overall average duration and min/max

layer_stats <- function(plot) {
 
    plot %>%
    add_lines(y = ~mean, name = "mean", color = I("Green")) %>%
    add_ribbons(ymin = ~min, ymax = ~max, name = "Min and Max", color = I("black"))
}


Stats <- read.csv("Stats.csv", sep=";", stringsAsFactors=FALSE)
Stats$Date <-as.POSIXct(Stats$DBegin, format = "%d/%m/%Y")
Stats$DBegin <-as.POSIXct(Stats$DBegin, format = "%d/%m/%Y %H:%M")
Stats$DEnd <-as.POSIXct(Stats$DEnd, format = "%d/%m/%Y %H:%M")
Stats$Duration<-chron(times=Stats$Duration)

Stats<- arrange(Stats,Server,Date,Apps)
ts <- summarise(group_by(Stats,Server,Date),total=sum(Duration),min = min(Duration, na.rm = TRUE),mean = mean(Duration, na.rm = TRUE),max = max(Duration, na.rm = TRUE))



```



## Some Basics Stats about the File


```{r kable, echo=F, warning=F, message=F}
library(knitr)
# kable(summary(Stats))
summary(Stats)
```


## Datas

After some grouping and summarizing with DPLYR,
the Datas:

```{r , echo=F, warning=F, message=F}

kable(head(ts))

```

## The Servers Activity

```{r, echo=F, warning=F, message=F}
allServers <- ts %>%
  plot_ly(x = ~Date, y = ~total) %>%
  add_lines(alpha = 0.5, name = "Applidis Servers", hoverinfo = "none")



allServers %>%
  add_fun(layer_stats)  %>%
  add_fun(layer_server, "SRVMV-COMMUN001") %>%
  add_fun(layer_server, "SRVMV-PDEP001")


```

## Conclusion

- With the interactive plot, we can see that SRVMV-COMMUN001 is globaly more  sougth than srvmv-pdep001
- It's just a a beginning and i intend to produce a full automatic report not only for the servers activity but also for applications and users



#MERCI !
(__Thank You in french__)




## Appendix: the code | the functions


```{r echo=T, eval=F, warning=F, message=F}


#loading the libraies
library(plotly)
library(chron)

# reusable function for highlighting a particular Serveur or app
layer_server <- function(plot, name) {
  plot %>% filter(Server == name) %>% add_lines(name = name)
}

# reusable function for plotting overall average duration and min/max

layer_stats <- function(plot) {
 
    plot %>%
    add_lines(y = ~mean, name = "mean", color = I("Green")) %>%
    add_ribbons(ymin = ~min, ymax = ~max, 
  name = "Min and Max", color = I("black"))
}

```
## Appendix | The File pre-processing code


```{r echo=T, eval=F, warning=F, message=F}
Stats <- read.csv("Stats.csv", sep=";", stringsAsFactors=FALSE)

Stats$Date <-as.POSIXct(Stats$DBegin, format = "%d/%m/%Y")

Stats$DBegin <-as.POSIXct(Stats$DBegin, format = "%d/%m/%Y %H:%M")
Stats$DEnd <-as.POSIXct(Stats$DEnd, format = "%d/%m/%Y %H:%M")
Stats$Duration<-chron(times=Stats$Duration)

Stats<- arrange(Stats,Server,Date,Apps)
ts <- summarise(group_by(Stats,Server,Date),total=sum(Duration),min = min(Duration, na.rm = TRUE),mean = mean(Duration, na.rm = TRUE),max = max(Duration, na.rm = TRUE))

summary(Stats)
head(ts)

```

## Appendix | The Plot code


```{r echo=T, eval=F, warning=F, message=F}
#The Plot

allServers <- ts %>%
  plot_ly(x = ~Date, y = ~total) %>%
  add_lines(alpha = 0.5, name = "Applidis Servers", hoverinfo = "none")

allServers %>%
  add_fun(layer_stats)  %>%
  add_fun(layer_server, "SRVMV-COMMUN001") %>%
  add_fun(layer_server, "SRVMV-PDEP001")


```



